---
title: "US Jail Population Analysis"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")

library(knitr)
```

## Introduction
This assignment focus on the prison racism in U.S. I want to analysis the 
different with region of black people population in jail
situation. I wonder how does the population relate with area.

## Summary Information
The average value for black jail population in urban area in 2018 is `r ave_black_pop_urban_2018` and the average value for black jail population in 
rural area in 2018 is `r ave_black_pop_rural_2018`.

`r highest_black_county` has the highest population of black people in jail 
through the years.

The average value for black jail population in urban area change over the last 
20 years is `r ave_change`.

The difference between highest black jail population in urban area and 
small/mid area is `r difference`.

## Charts
```{r, echo=FALSE, warning=FALSE, fig.width=16, fig.height=10, out.height= "50%"} 
chart_one
```
This chart shows the rural area has much more black people in the prison. And 
the population keep increase until 2008. The chart shows in 2018, both rural 
area and urban area, the black people population decrease.



```{r, echo=FALSE, warning=FALSE, fig.width=16, fig.height=10, out.height= "50%"} 
barplot(cbind(
  chart_two_data$white_pop_urban_2018, chart_two_data$black_pop_urban_2018), 
  main="white jail population vs black jail population", 
  ylab="Population", beside=TRUE)
```
These two bar chart compare the white people population in jail and white people population in jail with rural area. They have similar trend, but black people 
population always is the higher one.

```{r, echo=FALSE, warning=FALSE, fig.width=16, fig.height=10, out.height= "50%"} 
county_map

```
This county_map shows the black people population in jail in every county. We 
can tell from the map that urual area has a higher black people population in 
jail.
